### 2010-03-01 doc/tech_doc/a-rex/arex_tech_doc.tex
Limited shares explained in A-REX technical documentation

@@

@@

When XML file only is used to configure the A-REX, the transfer shares
can be implemented by defining \emph{maxLoadShare} (the limit itself)
and \emph{loadShareType} (the scheme used) elements inside 
\emph{loadLimits} block.

>>>>

\item \textbf{\textit{share\_limit}}\textit{=name limit} -- specifies a transfer
share that has a number of processes different from the default value in
maxloadshare. \emph{name} is the name of the share and \emph{limit} is the 
number of processes for this share. In the configuration should appear after 
maxloadshare. Can be repeated several times for different shares.
See Section~\ref{sub:Transfershare} for how to compose shares' names and more
details.

@@

It's possible to distinguish some transfer shares and assign them a limit
different from what's specified in \emph{maxloadshare}. It's done by
\emph{share\_limit} option. \emph{share\_limit} can only be used if 
\emph{maxloadshare} has been already set before. Depending on the 
sharing mechanism used by \emph{maxloadshare}, the proper name for the share
should be specified, as illustrated by the following examples (note, that
in dn case spaces are allowed, the configuration parser will take care of them):

\begin{itemize}
\item \emph{dn}: /O=Grid/O=NorduGrid/OU=domainname.com/CN=Jane Doe
\item \emph{voms:vo}: voname
\item \emph{voms:role}: voname:rolename
\item \emph{voms:group}: /voname/groupname
\end{itemize}

The specific shares, specified in \emph{share\_limit}, are processed
differently from the other shares. A-REX reserves an indicated number of 
processes for each specific share. The number of unreserved processes is then
split evenly between the ordinary shares, as determined by \emph{maxloadshare}. 
So the specific shares have a strict, non-decreaseable limit, unlike all the 
ordinary shares, whose limit can be decreased while A-REX tries to split the 
load evenly. However, A-REX reserves processes only for active 
specific shares, i.e. shares to which at least one active job on the resource 
belongs to. If the share is not active, its slots are used in overall splitting
between ordinary transfer shares.

A particular case is when A-REX reserves more processes than specified in
\emph{maxjobs}. A-REX will process jobs from specific share at FIFO-basis and
stop at reaching \emph{maxjobs} number of processes, even if some specific
shares haven't reached their limits. Also in this situation each ordinary
share is allowed to launch only one upload and download process.

@@

When XML file only is used to configure the A-REX, the transfer shares
can be implemented by defining \emph{maxLoadShare} (the limit itself)
and \emph{loadShareType} (the scheme used) elements inside 
\emph{loadLimits} block. For defining the specific shares, \emph{shareLimit}
sub-blocks with \emph{name} and \emph{limit} elements can be used after 
\emph{maxLoadShare}.
